Human Capital Model

### 2015-02-09 paper.tex
change environment

\documentclass[12pt,a4paper,titlepage]{article}
%\usepackage[doublespacing]{setspace}
\usepackage[utf8]{inputenc}         %This is used for ASKII digits.
\usepackage{amsmath, amssymb}       %This is for mathematic statements,check"amath.colorado.edu/documentation/LaTex/Symbols.pdf"
\usepackage{amsfonts,mathrsfs}      %fonts~~
\usepackage{graphicx}               %This is for graph inserting.
\usepackage{paralist}               %Give me compact lists!!!!! 'compactitem' 'compactenum' 'compactdesc'
%\usepackage{bm}                     %various kinds of bold texts.
\usepackage[top =2.54cm, bottom =2.54cm, left =3.18cm, right =3.18 cm]{geometry}
\usepackage{indentfirst}            %Indent the first letter
\usepackage{fancyhdr}               %Below is the head of the article.
\pagestyle{fancy}
\usepackage{booktabs}
\usepackage{lastpage}
\lhead{Team \# 33131}
\rhead{Page \thepage{} of \pageref{LastPage}}
\cfoot{}
%\numberwithin{equation}{section}    %Numbering of the equations will be based on sections.
%\usepackage{amsthm}
%\theoremstyle{definition}
%\newtheorem{def}{Definition}  %Below set the theorem system.
%\theoremstyle{plain}
%\newtheorem{thm}[law]{Thm}
%\theoremstyle{remark}
%\newtheorem*{remark}{Remark}
\newcommand{\boldit}[1]{\textbf{\textit{#1}}}
\usepackage{float}
\usepackage{paralist}
\usepackage{url}

@@

\section{Assumptions and Justifications}
\label{sec:assumptions-and-justifications}

@@

The possibility of the unforeseen accidents, which could force an
employee to leave his position,is neglected.Human nature, an employee
will stay at his position to chase for higher level.

\item \textbf{assumption 2} For a vacancy,if there exists an
  employee measures up to it already,ICM won't recruit for it.

Since recruiting good people is difficult, time consuming and
expensive according to issue 5,it is wasteful to recruit for a
position if an employee can promote to it.

@@

\item \textbf{assumption 5} For the promotion probability and
  organization change, the other factors effects the churn probability
  is invariable.

Though churn derives from varieties of reasons and they are actually
lacking of known conditions and data to estimate them, we have to
regard it as stable in our model.

\item \textbf{assumption 6} Each division or office have at least one
  middle manager or senior manager.

@@

Definitions of symbols employed in this paper are listed in
\textbf{Table 1}.
\begin{table}
\begin{tabular}{|l|l|}
  Variable & Description \\
  \hline
  $i$            &Index of an employee \\
  $L_{i,t}$          &The level of $i$ \\
  $s_{ij,t}$        &The relation strength from $i$ to $j$ \\
  $a_{ij,t}$        &Represent the influence caused by relationship
                    between superior and subordinate \\
  $f_{ij,t}$        &Represent the influence caused by relationship
                    between person with many friends and person with
                    few friends \\
  $c_{i,t}$        &Clustering Coefficient of $i$
\end{tabular}
\end{table}

@@

The meaning of the number in each cell is explained in []. The numbers
themselves are based on our own subjective decisions.

We then get the weight of each factor by calculating the bigest
eigenvalue and it's corresponding eigenvector, as given in Table.

\begin{center}
\begin{tabular}{c|cccc}
  Factor  &$A_{ac}$    &$A_{ab}$   &$A_{at}$    &$A_{po}$\\ \hline
  Weight  &0.3805  &0.0709  &0.2371  &0.3030\\
\end{tabular}
\end{center}

We test the consistency of the preferences for this instance of the
AHP. For good consistency [Alonso and Lamata 2006, 446 - 447]:

@@

Finally, we explain the concept of clustering coefficient [Duncan
J. Watts and Steven Strogatz 1998] of $i$ denoted as $c_{i,t}$, which
is a measure of the degree to which nodes in a graph tend to cluster
together. $c_{i,t}$ is defined as:

@@

\begin{itemize}
\item [\textit{step 1}] Promotion: If there's a vacancy in superior
  and $i$ has the ability to occupy this position, let $L_{i+1,t} =
  L_{i,t}+1$ with probability mentioned above and build edges between
  $i$ and his new colleagues.
\item [\textit{step 2}] Churn: If $i$ isn't promoted, he will have the
  probability to churn with a churn rate $l$.
\item [\textit{step 3}] Stay: If $i$ hasn't been promoted or churned,
  he will keep his job and do nothing.
\end{itemize}

@@

@@

\subsection{Analysis for Task 2}
\label{sec:analysis-for-task-2}

@@

To maintain enough employees, the company has to spend more on recruiting. So high turnover rate directly increase the recruiting budget. High turnover rate's effect on training budget and salary budget is more complex. On the one hand, when churn rate goes up, vacancies in the middle level keeps rising due to long recruiting time and low promote rate. On the other hand, the vacancies in lower level remains low because of the short recruiting time. So the full rate of the company decreases when churn rate rises. Since training budget and salary budget are closely related to full rate, both of them decrease when turnover rate goes up.
\subsection{Analysis for Task 5}
\label{sec:analysis-for-task-5}

>>>>

\documentclass[12pt,a4paper,titlepage]{article}
%\usepackage[doublespacing]{setspace}
\usepackage[utf8]{inputenc}         %This is used for ASKII digits.
\usepackage{amsmath, amssymb}       %This is for mathematic statements,check"amath.colorado.edu/documentation/LaTex/Symbols.pdf"
\usepackage{amsfonts,mathrsfs}      %fonts~~
\usepackage{graphicx}               %This is for graph inserting.
\usepackage{paralist}               %Give me compact lists!!!!! 'compactitem' 'compactenum' 'compactdesc'
%\usepackage{bm}
\usepackage{caption2}                 %various kinds of bold texts.
\usepackage[top =2.54cm, bottom =2.54cm, left =3.18cm, right =3.18 cm]{geometry}
\usepackage{indentfirst}            %Indent the first letter
\usepackage{fancyhdr}               %Below is the head of the article.
\pagestyle{fancy}
\usepackage{booktabs}
\usepackage{lastpage}
\lhead{Team \# 33131}
\rhead{Page \thepage{} of \pageref{LastPage}}
\cfoot{}
%\numberwithin{equation}{section}    %Numbering of the equations will be based on sections.
%\usepackage{amsthm}
%\theoremstyle{definition}
%\newtheorem{def}{Definition}  %Below set the theorem system.
%\theoremstyle{plain}
%\newtheorem{thm}[law]{Thm}
%\theoremstyle{remark}
%\newtheorem*{remark}{Remark}
\newcommand{\boldit}[1]{\textbf{\textit{#1}}}
\usepackage{float}
\usepackage{paralist}
\usepackage{url}

@@

\subsection{Assumptions and Justifications}
\label{sec:assumptions-and-justifications}

@@

The possibility of the unforeseen accidents, which could force an
employee to leave his position, is neglected. Based on human nature,
an employee will stay at his position to chase for higher level.

\item \textbf{assumption 2} For a vacancy,if there exists an
  employee measures up to it already, ICM won't recruit for it.

Since recruiting good people is difficult, time consuming and
expensive according to issue 5, it is wasteful to recruit for a
position if an employee can promote to it.

@@

\item \textbf{assumption 5} Each division or office have at least one
  middle manager or senior manager.

@@

Definitions of symbols employed in this section are listed in Table
\ref{variable1}:
\begin{table}
  \centering
  \begin{tabular}{l p{10cm}}
  \toprule{}
  Variable & Description \\
  \midrule{}
  $i$            &Index of an employee \\
  $L_{i,t}$          &The level of $i$ \\
  $s_{ij,t}$        &The relation strength from $i$ to $j$ \\
  $a_{ij,t}$        &Represent the influence caused by relationship
                    between superior and subordinate \\
  $f_{ij,t}$        &Represent the influence caused by relationship
                    between person with many friends and person with
                    few friends \\
  $c_{i,t}$        &Clustering Coefficient of $i$ \\ \bottomrule{}
\end{tabular}
\caption{Variables and Descriptions}\label{variable1}
\end{table}

@@

The meaning of the number in each cell is explained in Figure
\ref{important}. The numbers themselves are based on our own
subjective decisions.

\begin{table}[htb]
  \centering
  \begin{tabular}{cl}
    \toprule{}
    Intensity of Importance&Definition \\ \midrule{}
    1                      &Equal Importance \\
    2                      &Weak or slight \\
    3                      &Moderate importance \\
    4                      &Moderate plus \\
    5                      &Strong importance \\
    6                      &Strong plus \\
    7                      &Very strong or demonstrated importance \\
    8                      &Very, Very strong \\
    9                      &Extreme importance \\ \bottomrule{}
  \end{tabular}
  \caption{The fundamental scale of absolute numbers}\label{important}
\end{table}

We then get the weight of each factor by calculating the bigest
eigenvalue and it's corresponding eigenvector, as given in Table \ref{weight}.

\begin{table}
\begin{center}
\begin{tabular}{ccccc} \toprule{}
  Factor  &$A_{ac}$    &$A_{ab}$   &$A_{at}$    &$A_{po}$\\ \midrule{}
  Weight  &0.3805  &0.0709  &0.2371  &0.3030\\ \bottomrule{}
\end{tabular}
\end{center}
\caption{Weight for factors}\label{weight}
\end{table}

We test the consistency of the preferences for this instance of the
AHP.\@ For good consistency [Alonso and Lamata 2006, 446 - 447]:

@@

@@

\begin{itemize}
\item [\textit{step 1}] Promotion: If there's a vacancy in superior
  and $i$ has the ability to occupy this position, let $L_{i+1,t} =
  L_{i,t}+1$ with probability mentioned above and build edges between
  $i$ and his new colleagues.
\item [\textit{step 2}] Churn: If $i$ isn't promoted, he will have the
  probability to churn with a churn rate $l$.
\item [\textit{step 3}] Stay: If $i$ hasn't been promoted or churned,
  he will keep his job and do nothing.
\item [\textit{step 4}] Recruit: Recruit for vacancies when all the
  employees have done these 3 steps above.
\end{itemize}

\section{The Improved Model}
\label{sec:the-improved-model}

\subsection{Assumptions and Justifications}

\begin{itemize}
\item \textbf{assumption 1} For the promotion probability and
  organization change, the other factors effects the churn probability
  is invariable.

Though churn derives from varieties of reasons and they are actually
lacking of known conditions and data to estimate them, we have to
regard it as stable in our model.
\end{itemize}

\subsection{Organizational Churn}

@@

\subsection{Productivity}

First, we explain the concept of clustering coefficient [Duncan
J. Watts and Steven Strogatz 1998] of $i$ denoted as $c_{i,t}$, which
is a measure of the degree to which nodes in a graph tend to cluster
together. $c_{i,t}$ is defined as:

@@

@@

To maintain enough employees, the company has to spend more on
recruiting. So high turnover rate directly increase the recruiting
budget. High turnover rate's effect on training budget and salary
budget is more complex. On the one hand, when churn rate goes up,
vacancies in the middle level keeps rising due to long recruiting time
and low promote rate. On the other hand, the vacancies in lower level
remains low because of the short recruiting time. So the full rate of
the company decreases when churn rate rises. Since training budget and
salary budget are closely related to full rate, both of them decrease
when turnover rate goes up.

\subsection{Analysis for Task 5}
\label{sec:analysis-for-task-5}
